### 2020-06-29 Thesis-Chapter2-Background.tex
Add a note on CFAA follow up
Add article on Chinese intelligence law
Resume work!

% FIXME: Kristen doesn't like the wording; also remove word "electronic"?
Encryption's dual role as enabler of strong privacy and cornerstone of computer security may be the central conflict in
the EA debate. Those who focus on its role in privacy object to its absolute power. Those who focus on its role in
security rely on its absolute power.

@@

% (the FBI almost lost some provisions; follow up on https://apnews.com/110ff653e98478da66765897dde3d613,
%     https://www.washingtontimes.com/news/2020/mar/15/adam-schiff-fisa-reform-intervention-protects-fbi-/,
%     https://saraacarter.com/fisa-senate-passes-measure-extending-surveillance-powers-abuses-not-addressed/)

@@

%     \law{1986}{\acf{CFAA}}{hughes_hr4718_1986}{
% Criminalized ``knowingly access[ing] a computer without authorization or exceeding authorized access'' and thereby
% violating the confidentiality, integrity, or availability of the system. While presumably intended to target hacking,
% the \acs{CFAA} has been used to prosecute a host of crimes, and suffers from dated language;
% % --what does it mean to ``access'' a ``computer'' loading a simple webpage may involve dozens of devices--
% whether violating the terms of service constitutes ``exceeding authorized access'' remains an open question
% \cite{wolff_computer_2016}. Importantly for \ac{EA}, the law includes carve-outs for law enforcement and intelligence
% activities.
% }

@@

@@

>>>>

% FIXME: Kristen doesn't like the wording
Encryption's dual role as enabler of strong privacy and cornerstone of computer security may be the central conflict in
the EA debate. Those who focus on its role in privacy object to its absolute power. Those who focus on its role in
security rely on its absolute power.

@@

% (the FBI almost lost some provisions; follow up on https://apnews.com/110ff653e98478da66765897dde3d613,
%     https://www.washingtontimes.com/news/2020/mar/15/adam-schiff-fisa-reform-intervention-protects-fbi-/,
%     https://saraacarter.com/fisa-senate-passes-measure-extending-surveillance-powers-abuses-not-addressed/)
% May 27: renewal in great doubt; Trump opposed because he sees himself as a victim of FISA abuse
%     (https://apnews.com/c04a5e3bb156774af83b686bbe2ea872)

@@

%     \law{1986}{\acf{CFAA}}{hughes_hr4718_1986}{
% Criminalized ``knowingly access[ing] a computer without authorization or exceeding authorized access'' and thereby
% violating the confidentiality, integrity, or availability of the system. While presumably intended to target hacking,
% the \acs{CFAA} has been used to prosecute a host of crimes, and suffers from dated language;
% % --what does it mean to ``access'' a ``computer'' loading a simple webpage may involve dozens of devices--
% whether violating the terms of service constitutes ``exceeding authorized access'' remains an open question
% \cite{wolff_computer_2016}. Importantly for \ac{EA}, the law includes carve-outs for law enforcement and intelligence
% activities.
%
% Follow up: CFAA going before supreme court: https://www.cyberscoop.com/cfaa-will-soon-day-supreme-court/
% }

@@

\subsubsection{The Judicial Environment}
\label{sec-us-judicial}

The above history and section on U.S. law encompasses the executive and legislative branches' influence on surveillance
and cryptography. A complete picture requires understanding the judiciary branch's influence via court rulings. The
judiciary branch exercises power through a framework based on AAAA and BBBB. In this section we analyze several
important cases and developments in the last few years.

% TODO: Framework for understanding judicial influence. See bergerson_judicial_1998 and gizzi_fourth_2016. Update the
%   "AAAA and BBBB" in the intro.

% TODO: Review historically important cases on the 1st, 4th, and 5th amendments, e.g. Katz v. United States, 1969.

% TODO: Review recent cases. See orenstein_2016, bittenbender_2019, vaas_2019.

@@

% TODO: China, see also blanchard_2017
